### 2018-12-04 Sections/physical_architectures_for_quantum_computing.tex
indexing

The simplest example of an easy such problem is coherent state linear optics\index{Coherent states!Linear optics}, as discussed in Sec.~\ref{sec:coherent_state_QC}. Taking this notion further, recall from Sec.~\ref{sec:exotic} that one of the phase-space\index{Phase-space} representations for generic optical states is the $P$-function\index{P-function}, which represents a density operator as a sum over coherent states,
\begin{align}
\hat\rho = \int\!\!\!\int P(\alpha) \ket{\alpha}\bra{\alpha} d^2\alpha.
\end{align}
Here $P(\alpha)$ is a quasi-probability function\index{Quasi-probability functions}. Importantly, iff the $P$-function is strictly non-negative, \mbox{$P(\alpha)\geq 0 \,\,\forall \,\alpha$}, the optical state may be trivially interpreted as a purely classical mixture of coherent states ($P(\alpha)$ would be a delta function for pure coherent states). If, on the other hand, the $P$-function exhibits negativity for any $\alpha$, this interpretation breaks down and is indicative of the state exhibiting non-classical\index{Non-classical states} behaviour.

@@

Until now we have focussed on optical systems where quantum information is encoded into discrete variables\index{Discrete-variables}, such as photon-number or polarisation. However, quantum states of light can also be considered in terms of continuous-variables (CVs)\index{Continuous-variables} in phase-space\index{Phase-space}.

@@

\subsubsection{Phase-shifters}\index{Phase-shifters}\index{Phase-space rotations}

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$ about the origin, implementing the transformation between the position and momentum operators,
\begin{align}\label{eq:xp_theta}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in position/momentum space.

@@

A Josephson junction \cite{bib:josephson1974the} comprises two bulk superconducting materials\index{Superconductors}, separated by a thin layer of insulating material\index{Insulators}. In the superconducting phase the superconductors contain Cooper-pairs\index{Cooper-pairs}, composed of paired electrons. These Cooper-pairs move from one superconducting layer to another through the insulating layer via quantum tunnelling\index{Tunnelling}. The quantum mechanical nature of Josephson junctions is determined by two important energy scales:
\begin{itemize}
\item Josephson coupling energy, $E_{J}$.\index{Josephson!Coupling energy}
\item Coulomb energy, $E_C$.\index{Coulomb!Energy}
\end{itemize}
The ratio between these two energy scales determines the energy spectrum of the superconducting qubit. This yields three distinct types of qubits:
\begin{itemize}
\item Voltage-driven charge qubits \cite{bib:bouchiat1998quantum, bib:nakamura1999coherent}.\index{Charge!Qubits}
	\item Flux-driven flux qubits \cite{bib:friedman2000quantum, bib:van2000quantum}.\index{Flux!Qubits}
	\item Current-driven phase qubits \cite{bib:martinis2002rabi}.\index{Phase qubits}
\end{itemize} 
These circuits and energy level diagrams for these are illustrated in Fig.~\ref{fig:superconductor_circuits}.

@@

\subsubsection{Phase qubits}\index{Phase qubits}

@@

The Hamiltonian of a phase qubit is,
\begin{align}
\hat{H} = E_{C} \hat{p}^{2} - I \phi_{0} \hat\delta - I_{0} \phi_{0} \cos \hat\delta,
\label{eq:phase_qubit_hamiltonian}
\end{align}
where $\hat\delta$ is the gauge invariant\index{Gauge invariance} phase-difference operator\index{Phase-difference operator} and the charge on the capacitor is $2pe$. These operators are conjugate variables, satisfying the commutation relation,
\begin{align}
	[\hat\delta, \hat{p}] = i \hbar.
\end{align}

>>>>

The simplest example of an easy such problem is coherent state linear optics\index{Coherent states!Linear optics}, as discussed in Sec.~\ref{sec:coherent_state_QC}. Taking this notion further, recall from Sec.~\ref{sec:exotic} that one of the phase-space\index{Phase!Space} representations for generic optical states is the $P$-function\index{P-function}, which represents a density operator as a sum over coherent states,
\begin{align}
\hat\rho = \int\!\!\!\int P(\alpha) \ket{\alpha}\bra{\alpha} d^2\alpha.
\end{align}
Here $P(\alpha)$ is a quasi-probability function\index{Quasi-probability functions}. Importantly, iff the $P$-function is strictly non-negative, \mbox{$P(\alpha)\geq 0 \,\,\forall \,\alpha$}, the optical state may be trivially interpreted as a purely classical mixture of coherent states ($P(\alpha)$ would be a delta function for pure coherent states). If, on the other hand, the $P$-function exhibits negativity for any $\alpha$, this interpretation breaks down and is indicative of the state exhibiting non-classical\index{Non-classical states} behaviour.

@@

Until now we have focussed on optical systems where quantum information is encoded into discrete variables\index{Discrete-variables}, such as photon-number or polarisation. However, quantum states of light can also be considered in terms of continuous-variables (CVs)\index{Continuous-variables} in phase-space\index{Phase!Space}.

@@

\subsubsection{Phase-shifters}\index{Phase!Shifts}\index{Phase!Space!Rotations}

A phase-shifter\index{Phase!Shifts}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$ about the origin, implementing the transformation between the position and momentum operators,
\begin{align}\label{eq:xp_theta}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in position/momentum space.

@@

A Josephson junction \cite{bib:josephson1974the} comprises two bulk superconducting materials\index{Superconductors}, separated by a thin layer of insulating material\index{Insulators}. In the superconducting phase the superconductors contain Cooper-pairs\index{Cooper-pairs}, composed of paired electrons. These Cooper-pairs move from one superconducting layer to another through the insulating layer via quantum tunnelling\index{Tunnelling}. The quantum mechanical nature of Josephson junctions is determined by two important energy scales:
\begin{itemize}
\item Josephson coupling energy, $E_{J}$.\index{Josephson!Coupling energy}
\item Coulomb energy, $E_C$.\index{Coulomb!Energy}
\end{itemize}
The ratio between these two energy scales determines the energy spectrum of the superconducting qubit. This yields three distinct types of qubits:
\begin{itemize}
\item Voltage-driven charge qubits \cite{bib:bouchiat1998quantum, bib:nakamura1999coherent}.\index{Charge!Qubits}
	\item Flux-driven flux qubits \cite{bib:friedman2000quantum, bib:van2000quantum}.\index{Flux!Qubits}
	\item Current-driven phase qubits \cite{bib:martinis2002rabi}.\index{Phase!Qubits}
\end{itemize} 
These circuits and energy level diagrams for these are illustrated in Fig.~\ref{fig:superconductor_circuits}.

@@

\subsubsection{Phase qubits}\index{Phase!Qubits}

@@

The Hamiltonian of a phase qubit is,
\begin{align}
\hat{H} = E_{C} \hat{p}^{2} - I \phi_{0} \hat\delta - I_{0} \phi_{0} \cos \hat\delta,
\label{eq:phase_qubit_hamiltonian}
\end{align}
where $\hat\delta$ is the gauge invariant\index{Gauge invariance} phase-difference operator\index{Phase!Difference operator} and the charge on the capacitor is $2pe$. These operators are conjugate variables, satisfying the commutation relation,
\begin{align}
	[\hat\delta, \hat{p}] = i \hbar.
\end{align}

### 2018-12-04 Sections/protocols_for_the_quantum_internet.tex
indexing

Coherent states (Sec.~\ref{sec:coherent_state_enc}), although not strictly \textit{quantum} states, nonetheless find broad applications in quantum protocols, for example as the pump for SPDC\index{Spontaneous parametric down-conversion (SPDC)} sources (Sec.~\ref{sec:single_phot_src}), or as a phase-reference\index{Phase-reference} for homodyne detection (Sec.~\ref{sec:homodyne})\index{Homodyne detection}. Coherent states are rather trivial to prepare, as they are closely approximated by laser sources. Despite their triviality, high quality lasers can nonetheless become very expensive, large, and inaccessible to the not-so-well-resourced end-user. It is not uncommon for laser sources in contemporary labs to be valued in the \$100k's.

@@

A homodyne detector interferes a state with a coherent state on a beamsplitter, which acts as a phase-reference\index{Phase-reference}, before photo-detecting both output modes and taking the difference in the photon count-rates (Fig.~\ref{fig:homodyne}).

@@

Each individual beamsplitter in such a decomposition is an arbitrary $\mathrm{SU}(2)$ matrix acting on two photonic creation operators, $\hat{a}^\dag$ and $\hat{b}^\dag$,
\begin{align}\index{Beamsplitters}
\begin{pmatrix}
\hat{a}^\dag_\mathrm{out} \\
\hat{b}^\dag_\mathrm{out}
\end{pmatrix}=\begin{pmatrix}
U_{11} & U_{12} \\
U_{21} & U_{22}
\end{pmatrix}\begin{pmatrix}
\hat{a}^\dag_\mathrm{in} \\
\hat{b}^\dag_\mathrm{in}
\end{pmatrix}.
\end{align}
When operating in the polarisation basis, wave-plates\index{Wave-plates} enable the same transformation as beamsplitters do in dual-rail encoding. The phase-shifters implement the unitary operation,\index{Phase-shifters}
\begin{align}
\hat\Phi(\phi)=e^{-i\phi\hat{n}},
\end{align}
or equivalently in the Heisenberg picture,
\begin{align}
\hat{U}\hat{a}^\dag\hat{U}^\dag \to e^{-i\phi}\hat{a}^\dag,
\end{align}
for phase-shift $\phi$.

@@

Thus, jointly, the displacement and squeezing operators enable arbitrary translations and dilations in phase-space\index{Phase-space}. These operations form the basis for CV quantum computing schemes, to be discussed in more detail in Sec.~\ref{sec:CV_QC}.

@@

The goal of quantum metrology is to estimate an unknown phase\index{Phase estimation} with the greatest degree of precision. This finds many applications, perhaps most notably the recent gravity wave measurement protocols \cite{???}. The shot-noise limit (SNL)\index{Shot-noise limit} represents the maximum achievable precision using classical states, whereas the Heisenberg limit (HL)\index{Heisenberg!Limit} is the best that can be achieved using quantum resources. The goal of quantum metrology is to beat the SNL, ideally saturating the HL.

>>>>

Coherent states (Sec.~\ref{sec:coherent_state_enc}), although not strictly \textit{quantum} states, nonetheless find broad applications in quantum protocols, for example as the pump for SPDC\index{Spontaneous parametric down-conversion (SPDC)} sources (Sec.~\ref{sec:single_phot_src}), or as a phase-reference\index{Phase!Reference} for homodyne detection (Sec.~\ref{sec:homodyne})\index{Homodyne detection}. Coherent states are rather trivial to prepare, as they are closely approximated by laser sources. Despite their triviality, high quality lasers can nonetheless become very expensive, large, and inaccessible to the not-so-well-resourced end-user. It is not uncommon for laser sources in contemporary labs to be valued in the \$100k's.

@@

A homodyne detector interferes a state with a coherent state on a beamsplitter, which acts as a phase-reference\index{Phase!Reference}, before photo-detecting both output modes and taking the difference in the photon count-rates (Fig.~\ref{fig:homodyne}).

@@

Each individual beamsplitter in such a decomposition is an arbitrary $\mathrm{SU}(2)$ matrix acting on two photonic creation operators, $\hat{a}^\dag$ and $\hat{b}^\dag$,
\begin{align}\index{Beamsplitters}
\begin{pmatrix}
\hat{a}^\dag_\mathrm{out} \\
\hat{b}^\dag_\mathrm{out}
\end{pmatrix}=\begin{pmatrix}
U_{11} & U_{12} \\
U_{21} & U_{22}
\end{pmatrix}\begin{pmatrix}
\hat{a}^\dag_\mathrm{in} \\
\hat{b}^\dag_\mathrm{in}
\end{pmatrix}.
\end{align}
When operating in the polarisation basis, wave-plates\index{Wave-plates} enable the same transformation as beamsplitters do in dual-rail encoding. The phase-shifters implement the unitary operation,\index{Phase!Shifts}
\begin{align}
\hat\Phi(\phi)=e^{-i\phi\hat{n}},
\end{align}
or equivalently in the Heisenberg picture,
\begin{align}
\hat{U}\hat{a}^\dag\hat{U}^\dag \to e^{-i\phi}\hat{a}^\dag,
\end{align}
for phase-shift $\phi$.

@@

Thus, jointly, the displacement and squeezing operators enable arbitrary translations and dilations in phase-space\index{Phase!Space}. These operations form the basis for CV quantum computing schemes, to be discussed in more detail in Sec.~\ref{sec:CV_QC}.

@@

The goal of quantum metrology is to estimate an unknown phase\index{Phase!Estimation} with the greatest degree of precision. This finds many applications, perhaps most notably the recent gravity wave measurement protocols \cite{???}. The shot-noise limit (SNL)\index{Shot-noise limit} represents the maximum achievable precision using classical states, whereas the Heisenberg limit (HL)\index{Heisenberg!Limit} is the best that can be achieved using quantum resources. The goal of quantum metrology is to beat the SNL, ideally saturating the HL.

### 2018-12-04 Sections/quantum_algorithms.tex
indexing

\subsection{Phase-estimation}\index{Phase-estimation!Algorithm}\label{sec:phase_est_alg}

@@

The quantum TDA algorithm then takes the simplicial complex mixed state and estimates the full set of Betti numbers by employing a phase-estimation algorithm\index{Phase estimation!Algorithm} (Sec.~\ref{sec:phase_est_alg}), which induces an exponential algorithmic runtime improvement. The full TDA algorithm is summarised in Alg.~\ref{alg:TDA}.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ShallowQuantumCircuits():
\begin{enumerate}
    \item Prepare the $n$-qubit state,
    \begin{align}
    \ket{\psi_\mathrm{in}} = \ket{0}^{\otimes n}.
    \end{align}
    \item Apply the $n$-qubit Hadamard transform\index{Hadamard!Transform},
    \begin{align}
    \hat{H}^{\otimes n}.
    \end{align}
    \item Apply the oracle,
	\begin{align}
		\hat{U}_q \ket{\vec x} = i^{q(\vec x)} \ket{\vec x},
	\end{align}
	for bit-string \mbox{${\vec x}\in \{0,1\}^{n}$}, composed of a product of CZ gates\index{Controlled-Z (CZ) gates} and phase-shifts\index{Phase-shift gates},
	\begin{align}
\hat{S}_i = \begin{pmatrix}
    1 & 0\\
    0 & -i
    \end{pmatrix}.
\end{align}
	\item Apply another $n$-qubit Hadamard transform,
    \begin{align}
    \hat{H}^{\otimes n}.
    \end{align}
    \item The output state is,
    \begin{align}
    \ket{\psi_\mathrm{out}} &= \hat{H}^{\otimes n}\cdot\hat{U}_q\cdot\hat{H}^{\otimes n}\ket{0}^{\otimes n}\nonumber\\
    &= \frac{1}{2^n}\sum_{\vec x,\vec z \in \{ 0,1\}^n} i^{q(\vec x)} (-1)^{\vec z^T \vec x}\ket{\vec z}.
    \end{align}
    \item Measure all qubits in the computational basis, yielding measurement outcomes \mbox{${\vec z}\in \{0,1\}^{n}$}, with probabilities,
    \begin{align}
   	 P(\vec z) = |\bra{\vec z}\hat{H}^{\otimes n}\cdot\hat{U}_q\cdot\hat{H}^{\otimes n}\ket{0}^{\otimes n}|^2.	
    \end{align}
	\item Repeat protocol \mbox{$O(\mathrm{poly}(n))$} times.
	\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket{0}} & \gate{{H}} & \multigate{2}{{U}_q} & \gate{{H}} & \meter \\
    \lstick{\vdots} & \gate{{H}} & \ghost{{U}_q} & \gate{{H}} & \meter \\
    \lstick{\ket{0}} & \gate{{H}} & \ghost{{U}_q} & \gate{{H}} & \meter \\
} \nonumber
\end{align}
}
\end{mdframed}
\captionspacealg \caption{Quantum computing using shallow circuits, where circuit depth scales as \mbox{$O(\log d)$}.} \label{alg:shallow_circs}
\end{table}

>>>>

\subsection{Phase-estimation}\index{Phase!Estimation!Algorithm}\label{sec:phase_est_alg}

@@

The quantum TDA algorithm then takes the simplicial complex mixed state and estimates the full set of Betti numbers by employing a phase-estimation algorithm\index{Phase!Estimation!Algorithm} (Sec.~\ref{sec:phase_est_alg}), which induces an exponential algorithmic runtime improvement. The full TDA algorithm is summarised in Alg.~\ref{alg:TDA}.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ShallowQuantumCircuits():
\begin{enumerate}
    \item Prepare the $n$-qubit state,
    \begin{align}
    \ket{\psi_\mathrm{in}} = \ket{0}^{\otimes n}.
    \end{align}
    \item Apply the $n$-qubit Hadamard transform\index{Hadamard!Transform},
    \begin{align}
    \hat{H}^{\otimes n}.
    \end{align}
    \item Apply the oracle,
	\begin{align}
		\hat{U}_q \ket{\vec x} = i^{q(\vec x)} \ket{\vec x},
	\end{align}
	for bit-string \mbox{${\vec x}\in \{0,1\}^{n}$}, composed of a product of CZ gates\index{Controlled-Z (CZ) gates} and phase-shifts\index{Phase!Shift gates},
	\begin{align}
\hat{S}_i = \begin{pmatrix}
    1 & 0\\
    0 & -i
    \end{pmatrix}.
\end{align}
	\item Apply another $n$-qubit Hadamard transform,
    \begin{align}
    \hat{H}^{\otimes n}.
    \end{align}
    \item The output state is,
    \begin{align}
    \ket{\psi_\mathrm{out}} &= \hat{H}^{\otimes n}\cdot\hat{U}_q\cdot\hat{H}^{\otimes n}\ket{0}^{\otimes n}\nonumber\\
    &= \frac{1}{2^n}\sum_{\vec x,\vec z \in \{ 0,1\}^n} i^{q(\vec x)} (-1)^{\vec z^T \vec x}\ket{\vec z}.
    \end{align}
    \item Measure all qubits in the computational basis, yielding measurement outcomes \mbox{${\vec z}\in \{0,1\}^{n}$}, with probabilities,
    \begin{align}
   	 P(\vec z) = |\bra{\vec z}\hat{H}^{\otimes n}\cdot\hat{U}_q\cdot\hat{H}^{\otimes n}\ket{0}^{\otimes n}|^2.	
    \end{align}
	\item Repeat protocol \mbox{$O(\mathrm{poly}(n))$} times.
	\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket{0}} & \gate{{H}} & \multigate{2}{{U}_q} & \gate{{H}} & \meter \\
    \lstick{\vdots} & \gate{{H}} & \ghost{{U}_q} & \gate{{H}} & \meter \\
    \lstick{\ket{0}} & \gate{{H}} & \ghost{{U}_q} & \gate{{H}} & \meter \\
} \nonumber
\end{align}
}
\end{mdframed}
\captionspacealg \caption{Quantum computing using shallow circuits, where circuit depth scales as \mbox{$O(\log d)$}.} \label{alg:shallow_circs}
\end{table}

### 2018-12-04 Sections/quantum_repeater_networks.tex
indexing

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the curvature of the Earth\index{Earth curvature}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell pairs\index{Bell!States}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variables!States}.

>>>>

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the curvature of the Earth\index{Earth curvature}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell pairs\index{Bell!States}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation!Encoding} single-photons or CV states\index{Continuous-variables!States}.

### 2018-12-04 Sections/the_quantum_space_race.tex
indexing

Currently there are only two satellites with the capability of sending and/or receiving photons through space: the Chinese QUESS\index{QUESS}, and the Japanese SOCRATES\index{Space Optical Communications Research Advanced Technology Satellite (SOCRATES)} satellites. In order to achieve world-wide coverage multiple communicating satellites will be necessary such that there be a constellation of satellites\index{Satellite constellation} that are visible at all times, anywhere on Earth, in a similar manner to the GPS satellite network\index{Global positioning system (GPS)}, thereby bypassing line-of-sight constraints, as per Fig.~\ref{fig:sat_constellation}.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{satellite_constellation}
	\captionspacefig \caption{Satellite constellation network for bypassing line-of-sight constraints in long-distance quantum communication. Neighbouring satellites connect via line-of-sight in space, and there are a sufficient number of satellites to enable global coverage such that all points on the Earth's surface are visible to at least one satellite at any given time, giving them indirect quantum access to any other point on the globe. In this simple example, entanglement swapping between satellites shares a Bell pair between Columbia and Tasmania, enabling the teleportation of certain Columbian products\index{Benzoylmethylecgonine} from Bogot{\'a} to the dance parties featuring at \href{https://soundcloud.com/peter-rohde}{DJ Rohde's} holiday home.\index{DJ Rohde}\index{Pablo Escobar}} \label{fig:sat_constellation}\index{Satellite constellation}
\end{figure}

>>>>

Currently there are only two satellites with the capability of sending and/or receiving photons through space: the Chinese QUESS\index{QUESS}, and the Japanese SOCRATES\index{Space Optical Communications Research Advanced Technology Satellite (SOCRATES)} satellites. In order to achieve world-wide coverage multiple communicating satellites will be necessary such that there be a constellation of satellites\index{Satellites!Constellations} that are visible at all times, anywhere on Earth, in a similar manner to the GPS satellite network\index{Global positioning system (GPS)}, thereby bypassing line-of-sight constraints, as per Fig.~\ref{fig:sat_constellation}.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{satellite_constellation}
	\captionspacefig \caption{Satellite constellation network for bypassing line-of-sight constraints in long-distance quantum communication. Neighbouring satellites connect via line-of-sight in space, and there are a sufficient number of satellites to enable global coverage such that all points on the Earth's surface are visible to at least one satellite at any given time, giving them indirect quantum access to any other point on the globe. In this simple example, entanglement swapping between satellites shares a Bell pair between Columbia and Tasmania, enabling the teleportation of certain Columbian products\index{Benzoylmethylecgonine} from Bogot{\'a} to the dance parties featuring at \href{https://soundcloud.com/peter-rohde}{DJ Rohde's} holiday home.\index{DJ Rohde}\index{Pablo Escobar}} \label{fig:sat_constellation}\index{Satellites!Constellations}
\end{figure}
